---
output:
  word_document: default
  html_document: default
---
---
  title: "SQING Tables and Figures"
  output: word_document
  
  ---
  
  ```{r include = FALSE}
  #devtools::install_github("crsh/papaja")
  library(varhandle)
  library(papaja)
  library(XLConnect)
  library(Hmisc)
  library(knitr)
  library(pander)
   library(dplyr)
  library(gridExtra)
  library(grid)
  require(pwr)
  
  #see https://www.r-bloggers.com/r-markdown-how-to-insert-page-breaks-in-a-ms-word-document/
  # https://www.r-bloggers.com/tables-from-r-into-word/
  # http://stackoverflow.com/questions/37671868/knitr-rmarkdown-docx-tables/37890832#37890832
  # https://ourcodingclub.github.io/2016/11/24/rmarkdown-1.html -re miktex/mactex
  #modified by Dorothy Bishop 4/2/17
  
  #username<-"pthompson"
  username<-"dorothybishop"
  
  locate1<-paste("C:\\Users\\",username,"\\Dropbox\\SQING\\excel sheets\\SQING_with_templates_230417.xlsx",sep="")
  
  if (username=="dorothybishop"){
    locate1<-paste("/Users/",username,"/Dropbox/Projects2016/SQING/excel sheets/SQING_with_templates_230417.xlsx",sep="")
    }
  
  SQING.dat=loadWorkbook(locate1)
  
  #create a data.frame with max number of columns from sheets by 30 rows
  
  ncols<-70
  nrows<-30
  allstudy<-data.frame(matrix(rep(NA,nrows*ncols),nrow=nrows)) #make data frame to hold all studies
  colnames(allstudy)=c('Study', 'Authors', 'Title', 'DOI', 'Sample', 'Sample_N', 'Subgroups', 
                       'Genes', 'Polymorphisms', 'Phenotypes', 'Analysis', 'SelResult', 'Conclusion', 
                       'SelRes_Variants_N', 'SelRes_ES', 'ES_source', 'Detect_ES_80', 'Power_ES_10', 
                       'Replication', 'Multcorr', 'Prevresults', 'Comment', 'Authorquery', 'Addinfo', 
                       'Geneticmodel', 'Haplotypes', 'N_Gmodels', 'CorrForN_Gmodels', 
                       'N_Polym', 'Correl_Polym', 'CorrForN_Polym','Genetic_analysis_notes', 'N_Pheno', 
                       'Correl_Pheno', 'CorrForN_Pheno', 'Neuro_Text', 'Neuro_CorrForN_approach','Imaging_Correction', 
                       'N_Neuropheno', 'CorrForN_Neuro', 'Mention_Multtest', 'Mention_ES', 
                       'Repcode', 'SelRes_N', 'Poldrack_80_Power', 'Au_contacted', 'Au_email', 'Au_response', 
                       'Detect_ES_80d', 'Neuro_Method', 'Quasi_ES', 'X7', 'X8', 'X9', 'X10','X11','X12','X13','X14','X15',
                       'X16','Journal','X19','X20')
  
  # add data from each study, reading from the specific sheet for that study
  for (i in 1:30){
    mysheet<-paste('overview_',i,sep='')
  
  temp=data.frame(readWorksheet(SQING.dat,sheet=mysheet,startCol=2,endCol=2,header=F))
  maxrow<-nrow(temp)
  
  if(maxrow>60){maxrow=60}
  allstudy[i,1:maxrow]=t(temp)
  #Add total N used to get selected result - in cells H4:H6
  temp2=data.frame(readWorksheet(SQING.dat,sheet=mysheet,startCol=8,endCol=8,startRow=4,endRow=6,header=F))
  allstudy[i,44]<-sum(temp2)
  }

 
# ------------------------------------------------------------------------------------------
# There was unexplained problem reading B15 (effect size) from some sheets - throws an error
# I think these were sheets where I had pasted figures _ i have moved them over and now seems OK
# ------------------------------------------------------------------------------------------
# Excel file did not have raw numbers for Discovery and Replication, so need to do these manually
# The original cell for N had text and this is now moved to column 62,
# The original subgroups column is also moved to column 63
# This means we can use columns 6 and 7 for numerical values for Discovery and Replication samples
allstudy$X19<-allstudy$Sample_N
colnames(allstudy)[63]<-'Sample_N_text'
allstudy$X20<-allstudy$Subgroups
colnames(allstudy)[64]<-'N_Subgroups'
temp<-readWorksheet(SQING.dat,sheet='Ns',startCol=3,endCol=4,header=F)
allstudy[,6]<-temp[,1]
allstudy[,7]<-temp[,2]
colnames(allstudy)[6:7]<-c('DiscoveryN','ReplicationN')
# ------------------------------------------------------------------------------------------
# Add journal names
temp<-readWorksheet(SQING.dat,sheet='studies_with_replicates',startCol=3,endCol=3,header=T)
allstudy$Journal[1:30]<-t(temp)
allstudy$Journal<-as.factor(allstudy$Journal)
# ------------------------------------------------------------------------------------------
# Add author response and email
temp<-readWorksheet(SQING.dat,sheet='authorcontact',startCol=4,endCol=5,header=T)
temp=temp[1:30,]
allstudy$Au_response<-temp[,1]
allstudy$Au_email<-temp[,2]
allstudy$Au_response<-as.factor(allstudy$Au_response)
levels(allstudy$Au_response)<-c('No reply','Acknowledged only','Responded','Other')
# ------------------------------------------------------------------------------------------
# Add replication code
temp<-readWorksheet(SQING.dat,sheet='studies_with_replicates',startCol=9,endCol=9,header=T)
temp=temp[1:30,]
allstudy$Repcode<-as.factor(temp)
levels(allstudy$Repcode)<-c('No','Yes','Other','Prior')

# ------------------------------------------------------------------------------------------

# Just for tidiness, ensure all text columns have initial capitalisation
textcols=c(5,11,19,20,22,28,32,36,42)
for (k in 1:length(textcols)){
allstudy[,textcols[k]]<-capitalize(allstudy[,textcols[k]])
}
# ------------------------------------------------------------------------------------------

# Ensure all Quasi_ES values are n/a (-1)  or No (0) or Yes (1)

allstudy$Quasi_ES<--1
temp=which(allstudy[,45]==1)
allstudy$Quasi_ES[temp]<-1
temp=which(allstudy[,45]==0)
allstudy$Quasi_ES[temp]<-0
allstudy$Quasi_ES<-as.factor(allstudy$Quasi_ES)
#we'll add more relevant factor names once we've used this for plot

allstudy$Imaging_Correction<-as.factor(allstudy$Imaging_Correction)
levels(allstudy$Imaging_Correction)<-c('Whole area a priori ROI','Peak within a priori ROI', 'ROI from data','n/a')
# Note that some columns are not now used because we did not have time to collect sufficient information. 
# These include:
# Prevresults, Authorquery, Addinfo (this is blank)
# ------------------------------------------------------------------------------------------
allstudy$Correl_Polym=as.factor(allstudy$Correl_Polym)
allstudy$Correl_Pheno<-as.factor(allstudy$Correl_Pheno)
levels(allstudy$Correl_Polym)<-levels(allstudy$Correl_Pheno)<-c('NA','Yes','Unclear','No')


allstudy$CorrForN_Polym=as.factor(allstudy$CorrForN_Polym)

levels(allstudy$CorrForN_Polym)<-c('No','Bonferroni','Data Reduction','Permutation','NA')

mytemp=which(allstudy$Genetic_analysis_notes==0) #tidying up text; replace 0 with - for this column
allstudy$Genetic_analysis_notes[mytemp]<-'-'
temp=which(allstudy$CorrForN_Pheno=='-')
allstudy$CorrForN_Pheno[temp]=5
allstudy$CorrForN_Pheno<-as.factor(allstudy$CorrForN_Pheno)
levels(allstudy$CorrForN_Pheno)<-c('None','Bonferroni', 'Permutation','Not needed')
# ------------------------------------------------------------------------------------------
# Recompute the power values for the SelRes_N
# (These have also been updated now in xls so should be the same )
for (i in 1:30){
  thisnum=as.integer(allstudy$SelRes_N[i])
  thispow=pwr.r.test(n=thisnum,sig.level =.05,power=.8,alternative="two.sided")
  result2= pwr.r.test(n =thisnum , sig.level =.05,r=.1,alternative="two.sided")
  thisr=thispow$r
  thisp=result2$power
  allstudy$Power_ES_10[i]=round(thisp,3)
  allstudy$Detect_ES_80[i]=round(thisr,3)
  myd=4/sqrt(thisnum)
  #myr=myd/sqrt(myd^2+4) Poldrack d to r
  allstudy$Poldrack_80_Power[i]=myd
  allstudy$Detect_ES_80d=myd
}


#Additional bit to explore neuro studies
allstudy$ID<-seq.int(nrow(allstudy))
mybit=data.frame(cbind(allstudy$ID, allstudy$Neuro_Text,allstudy$Neuro_CorrForN_approach,
                       allstudy$N_Neuropheno,allstudy$CorrForN_Neuro,allstudy$Repcode))
colnames(mybit)=c('ID','Neuro_Text,','Neuro_CorrForN_approach','N_Neuropheno','CorrForN_Neuro','Repcode')
nn=which(mybit$N_Neuropheno==0)
mybit=mybit[-nn,]
  
allN=seq(1:30)
neuroindex=allN [! allN %in% nn] #numbers of studies with neuro
allstudy$Neuro_Method=rep('-',30)
allstudy$Neuro_Method[neuroindex]=c('fMRI','fMRI','fMRI','VBM','Neuropathology','fMRI','Structural MRI','fMRI','fMRI','PET','Structural MRI','fMRI','fMRI','fMRI','Structural MRI+fMRI','fMRI')

#Check: compare Poldrack ES 80 with computed version from R
# plot(allstudy$Detect_ES_80,(4/sqrt(as.numeric(allstudy$SelRes_N))))

#Create a table with the Ns for multiple contrasts
myvars=c('Study','N_Subgroups','N_Polym','N_Gmodels','N_Pheno','N_Neuropheno','X16','Multcorr','Quasi_ES')
myNtable=allstudy[myvars]
mycombs<-as.integer(allstudy$N_Gmodels)*as.integer(allstudy$N_Polym)
temp<-as.integer(allstudy$N_Pheno)
temp[temp==0]<-1
mycombs<-mycombs*temp
temp<-as.integer(allstudy$N_Neuropheno)
temp[temp==0]<-1
mycombs<-mycombs*temp
temp<-as.integer(allstudy$N_Subgroups)
temp[temp==0]<-1
mycombs<-mycombs*temp
colnames(allstudy)[61]<-'Combinations'
colnames(myNtable)[7]<-'Combinations'
allstudy$Combinations<-mycombs
myNtable$Combinations<-mycombs
#Now mark those where models, pheno or genos are correlated 


temploc<-which(myNtable$N_Gmodels>1)
temp<-myNtable$N_Gmodels[temploc]
temp=paste(temp,"-",sep='')
myNtable$N_Gmodels[temploc] <- temp  

temploc<-which(allstudy$Correl_Polym=='Yes')
temp<-myNtable$N_Polym[temploc]
temp=paste(temp,"-",sep='')
myNtable$N_Polym[temploc] <- temp  

#add a minus to those where Phenotypes correlated
temploc<-which(allstudy$Correl_Pheno=='Yes')
temp<-myNtable$N_Pheno[temploc]
temp=paste(temp,"-",sep='')
myNtable$N_Pheno[temploc] <- temp

#add a tilde to those where Phenotypes probably correlated
temploc<-which(allstudy$Correl_Pheno=='Unclear')
temp<-myNtable$N_Pheno[temploc]
temp=paste(temp,"~",sep='')
myNtable$N_Pheno[temploc] <- temp 


#recycle Quasi-effect code to mark those with neuroimaging
temploc<-which(myNtable$N_Neuropheno > 0)
myNtable$Quasi_ES[temploc]<-9

myNtable$FullCorrect<-c(1,1,0,0,1,0,1,0,1,1,0,2,0,1,2,2,2,2,0,0,2,1,0,0,2,0,0,1,2,2)

#sort so all neuro together
#colnames(myNtable)[1]<-'Journal'
#myNtable$Journal<-allstudy$Journal
newNtable<-myNtable #Previously had option of sorting to group studies, but omitted here

#newNtable <- myNtable[order(as.integer(myNtable$Combinations)),] 
#newNtable <- newNtable[order(as.integer(newNtable$Quasi_ES)),] 

lastcol=length(colnames(newNtable))
newNtable<-newNtable[,-lastcol] #remove Quasi_ES column

colnames(newNtable)<-c('Journal','Subgroups','Models','Polymorphisms','Phenotypes','Imaging regions','All Combinations','Correction method')
write.table(newNtable, "mynewtable.txt", sep="\t") 

mynubit<-allstudy[,c(6,7,15,8)]
write.table(mynubit,'mynubit.txt',sep='\t')
```


#Table 1
Multiple comparisons

```{r, echo=FALSE}


kable(newNtable,caption='Corrections for multiple comparisons in relation to N subgroups, genetic models, polymorphisms, and imaging regions. All combinations is the product of all of these. – denotes correlated variables; ~ denotes probably correlated
')
```
***
#Figure 2
##Obtained effect size in relation to sample size (on log scale)
##Symbols denote replication: triangle = Prior, square = Yes, circle = No, diamond = Other.

```{r, echo=FALSE} 
#NB black are 'quasi' effect sizes: need a legend to show this
# Also would be good to show correlation coeff for log sample size vs ES

plot(allstudy$SelRes_N,allstudy$SelRes_ES, main="Log sample size by Effect size (r)",log='x',
    xlab="Sample size ", ylab="Effect size (r)", pch=(20+as.numeric(allstudy$Repcode)),
    bg=(1+151*allstudy$Quasi_ES))  
fullcorrel<-cor(log(as.numeric(allstudy$SelRes_N)),as.numeric(allstudy$SelRes_ES))
mysubset<-allstudy[allstudy$Quasi_ES==-1,]
subsetcorrel<-cor(log(as.numeric(mysubset$SelRes_N)),as.numeric(mysubset$SelRes_ES))

levels(allstudy$Quasi_ES)=c('n/a','No','Yes') #for Appendix
```

***
#Table 2 


```{r, echo=FALSE}

  temp=allstudy$N_Polym
temp2=which(temp>1)
temp[temp2]='Uncorrelated'
temp3=which(allstudy$Correl_Polym=="Yes")
temp[temp3]='Correlated'
tab1<-table(allstudy$CorrForN_Polym,temp)
nstudy<-sum(tab1[1:4,2:3])
kable(tab1[1:4,2:3],caption=paste('Correction for multiple testing in relation to genetic variants considered: ',nstudy,' studies with 2 or more correlated or uncorrelated polymorphisms',sep=''))
```

***

#Table 3


```{r, echo=FALSE}


tab3<-table(allstudy$CorrForN_Pheno,allstudy$Correl_Pheno)
kable(tab3,caption='Correction for multiple testing in relation to behavioural phenotypes')
```

***

#Table 4


```{r, echo=FALSE}
tab4<-table(allstudy$Journal,allstudy$Repcode)
kable(tab4,caption='Number of studies including replication sample, by journal')
```


***

#Appendices

```{r, echo=FALSE,results = 'asis'}
mytempx=matrix(rep(NA,2*71),ncol=2)
mytempx[1:71,1]=colnames(allstudy)# for checking col number of relevant columns
neworder<-c(3,4,62,13,5,6,7,8,9,29,30,10,33,34,39,11,25,27,50,12,16,44,22,15,51,38,41,28,31,35,37,17,18,48) #Authors omitted

  mytempl<-matrix(rep(NA,2*34),ncol=2)
  
  mytempl[1:34,1]<-c('Title', 'DOI', 'Journal','Conclusion','Sample', 'Discovery Sample N','Replication Sample N',
                     'Genes', 'Polymorphisms', 'N Polymorphisms','Correlated Polymorphisms','Phenotypes', 'N Behav. Phenotypes','Correlated Behav. Phenotypes','N Neuro Phenotypes','Analysis Method', 'Genetic models','N genetic models', 'Neuro methods','Selected Result', 'Selected Result Source','Ns for Selected Result','Comment on Selected Result','Selected Result Effect Size','Quasi Effect Size?','Imaging ROI approach','Mention of multiple comparisons','Correction for N genetic models','Correction for N polymorphisms','Correction for N behavioural phenotypes','Correction for N neuro phenotypes','Effect Size (r) Detectable with 80% Power','Power to Detect Effect Size (r) of .1','Author response to contact')
for (i in 1:30){
  thisstudy=paste('Study',i)
  #print(thisstudy)
  colnames(mytempl)=c('Information',thisstudy)
  mytempl[,2]<-t(allstudy[i,neworder])
print(kable(mytempl,caption='')) #Have to explicitly print if in a loop
 
 # print(grid.table(mytempl))
  #need to look at formatting with ftp://cran.r-project.org/pub/R/web/packages/gridExtra/vignettes/tableGrob.html

}

#anova according to replication status  
  require(ggplot2)
 
  allstudy$SelRes_ES=as.numeric(allstudy$SelRes_ES)
 ggplot(allstudy,aes(x=allstudy$Repcode,y=allstudy$SelRes_ES))+geom_boxplot(fill='grey80',colour='blue')+scale_x_discrete()+ xlab("Replication") +
  ylab("Effect size")
mymod1 = lm(SelRes_ES ~ Repcode, data =allstudy)